### 2009-11-29 doc/manuals/janitor/tex_installation/installation.tex
Merged janitor installation.tex of manual and tech_doc

The Janitor requires the two perl packages listed in
table~\ref{tab:install_dependencies}. To have
the WebService interface for the Janitor, the packages listed in the
table~\ref{tab:install_dependencies_optional} need to be installed before
the build process is. The Perl modules are available on CPAN and ship
with all major Linux distributions.

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for Janitor.}{Log4perl is used for the internal logging of Janitor, while the 
                   Redland RDF library is used for accessing the catalogue of Runtime Environments.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for the Janitor.}{The library libperl-dev provides the required header files to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

The Janitor will be installed by default along with ARC-NOX. Support for
the dynamic REs can be completely disabled at compile time by using
the \textit{configure} flags \textit{--disable-janitor-service} for
the complete janitor or \textit{--disable-janitor-webservice} to only
disable the Janitor's Web Service.

Furthermore it is recommended to install the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}}
in order to be to easily maintain the knowledge database of installable packages.
At the time of writing, no Linux distribution is offering packages for this fine tool.

@@

The current version of the Janitor can be configured using the
common file \textit{arc.conf}. It is expected in the configuration
directory \textit{etc}. The Janitor is using the environment
variable \textit{NORDUGRID\_CONFIG} to determine the location of the
corresponding file. If that variable is not set, the default location
\textit{/etc/arc.conf} will be used.  The configuration is assigned
by the section \lbrack janitor\rbrack. Table~\ref{tab:arc_conf_tags}
describes the available tags for Janitor's configuration.

@@

The parameter \texttt{enabled} specifies whether the Janitor shall be used
within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.\footnote{For
the time speaking, you need to have started the ARC services as root to
allow the Janitor to change into those IDs.} The \texttt{registrationdir}
describes the directory in which the subdirectories \texttt{jobs} and
\texttt{rtes} will be created.  In these directories the states of the
jobs and the runtime environments will be stored.  The knowledge base
of installable packages is specified by the parameter \texttt{catalog}.
Its value can be any kind of URL pointing to a file written in the
Resource Description Framework (RDF) format.  The specification of the
RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which
the installation files will be saved after they have been downloaded
or copied from the repository which was specified by the catalog. The
\texttt{installationdir} finally specifies the directory into which all
packages will be installed and should be available for all computing
elements, i.e.\ by using a shared volume.  If the configuration file
furthermore contains the \texttt{runtimedir} tag within the section
\texttt{grid-manager}, the Janitor will also create a symbolic link
in the \texttt{runtimedir} pointing to the configuration script of the
installation performed by the Janitor.  The tags \texttt{jobexpirytime}
and \texttt{rteexpirytime} are used for an automated cleanup and is
defined in seconds.  The default value for the \texttt{jobexpirytime} is
seven days and for the \texttt{rteexpirytime} three days.  The additional
tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if
the catalog is maintained by a higher organization.  The path to the
log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the
Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

The Janitor is designed to be used on Linux distributions.
Its porting to other platforms has not yet been addressed.

@@

% Is designed for linux distributions. Windows or Mac won't work (Reason wget! maybe also the Executer).

>>>>

The Janitor requires the two perl packages listed in
table~\ref{tab:install_dependencies}. To have the WebService
interface for the Janitor, the packages listed in
table~\ref{tab:install_dependencies_optional}
need to be installed before
the build process is. The Perl modules are available on CPAN and ship
with all major Linux distributions.  
\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for the Janitor.
		   Log4perl is used for the internal logging of the
		   Janitor, while the Redland RDF library is used
		   for accessing the knowledge base (catalog) of
		   Runtime Environments.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for the Janitor.}{The
		   library libperl-dev provides the required header files to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

If you are using regular Debian or Ubuntu packages, then the Janitor
can be installed as root by "apt-get install nordugrid-arc1-janitor".
Installing it will not drag other components of ARC with it since the
Janitor can be used in its own right or in conjunction with another
grid system, possibly. Packages for Redhat/Fedora and SuSE/OpenSuSE are
also provided, the redland library however may not yet be available for
those systems.

The Janitor source code is shipped as a part of the regular ARC-NOX
source tree.  If you are compiling the sources yourself, the default
is to have the A-REX grid manager technically prepared to interact
with the Janitor.
The interaction can be prohibited
with the \textit{configure} flags \textit{--disable-janitor-service}
for the complete janitor or \textit{--disable-janitor-webservice} for
only the Web Service support.

Furthermore it is recommended to install the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}}
in order to be to easily maintain the knowledge database of installable
packages.  At the time of writing, no Linux distribution is offering
packages for this fine tool. The basic editing can also be performed
fairly easily without that tool, but one is unlikely to use the technology
to its full potential, then.

@@

The current version of the Janitor can be configured using the
common file \textit{arc.conf}. It is expected in the configuration
directory \textit{etc}. The Janitor is using the environment
variable \textit{NORDUGRID\_CONFIG} to determine the location of the
corresponding file. If that variable is not set, the default location
\textit{/etc/arc.conf} will be used.  The configuration is assigned
by the section \lbrack janitor\rbrack. Table~\ref{tab:arc_conf_tags}
describes the available tags for the Janitor's configuration.

@@

The parameter \texttt{enabled} specifies whether the Janitor shall be used
within A-REX or not. This needs to be distinguished from the previously mentioned
compilation flags of a similar name. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.

The \texttt{registrationdir} describes the directory in which the
subdirectories \texttt{jobs} and \texttt{rtes} will be created.
In these directories the states of the jobs and the runtime environments
are stored. Please recall that the Janitor does not use a database as
a backend, but all communication between invocations are performed via
files in those folders.

The knowledge base of installable packages is specified by the parameter
\texttt{catalog}.  Its value can be any kind of URL pointing to a file
written in the Resource Description Framework (RDF) format.  One should
not light-heartedly use a remote address for this purpose. Such a remote
source needs to be trusted, since any runtime environment specified in
a catalog (if the package description matches constraints by the local
site administrator) may possibly be installed by regular grid users.

The specification of the RDF file will be explained in detail in
section~\ref{sec:catalog}.  The parameter \texttt{downloaddir} assigns
the directory to which the installation files will be saved after they
have been downloaded or copied from the repository which was specified by
the catalog. Please remember: the URL in arc.conf indicates the location
of the catalog. And the URLs somehow specified in the catalog specify
the location from where to download the runtime environment.

The \texttt{installationdir} finally specifies the directory into which
all packages will be installed. This directory needs to be available
for all computing nodes for the execution of arbitrary programs, most
commonly by using it as a shared NFS volume.

If the configuration file furthermore contains the \texttt{runtimedir}
tag within the section \texttt{grid-manager}, the Janitor will also
create a symbolic link in the \texttt{runtimedir} pointing to the
configuration script of the installation performed by the Janitor.
The tags \texttt{jobexpirytime} and \texttt{rteexpirytime} are used
for an automated cleanup and is defined in seconds.  The default
value for the \texttt{jobexpirytime} is seven days and for
the \texttt{rteexpirytime} three days.  The additional tags
\texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if the
catalog is maintained by a higher organization. But again: you need to
trust it.

The path to the log4perl configuration file is defined by the tag
\texttt{logconf}.  Examples on how to configure ARC and log4perl are
provided in the Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

The Janitor was designed to be used for UNIX-compatible operating systems
and tested for various Linux distributions. It should also be functional
on MaxOS X and Windows with Cygwin / CoLinux.  The porting of the Janitor
to other platforms has not yet been addressed.

@@
